\begin{activity} \label{A:9.6.3} Vector-valued functions can be used to generate many interesting curves. Graph each of the following using an appropriate tool\footnote{e.g., the 2D grapher at \url{http://webspace.ship.edu/msrenault/ggb/parametric_grapher.html}, or for 3D graphs Wolfram$\mid$Alpha, an on-line 3D grapher like \url{http://www.math.uri.edu/~bkaskosz/flashmo/parcur/}, or some other device}, and then write one sentence for each function to describe the behavior of the resulting curve.
	\ba
	\item $\vr(t) = \langle t\cos(t), t\sin(t) \rangle$

	\item $\vr(t) = \langle \sin(t)\cos(t), t\sin(t) \rangle$

	\item $\vr(t) = \langle t^2\sin(t)\cos(t), 0.9t\cos(t^2), \sin(t) \rangle$
	
	\item $\vr(t) = \langle \sin(5t), \sin(4t) \rangle$

	\item Experiment with different formulas for $x(t)$ and $y(t)$ and ranges for $t$ to see what other interesting curves you can generate.  Share your best results with peers.

	\ea

\end{activity}
\begin{smallhint}

\end{smallhint}
\begin{bighint}

\end{bighint}
\begin{activitySolution}
	\ba
	\item The graph of $\langle \cos(t), \sin(t) \rangle$ is the unit circle, so the multiple $t$ will make the graph of $\vr(t) = \langle t\cos(t), t\sin(t) \rangle$ be a spiral whose radii increase as $t$ increases. 
	
	\item The factor of $\sin(t)$ will make the $x$-coordinate oscillate while the factor $t$ makes the $y$-coordinate increase. The resulting graph is a series of figure eight's constrained on $-1 \leq x \leq 1$ with increasing radii in the $y$ direction as $t$ increases. 

	\item This is just crazy. 
	
	\item This is an example of a \emph{Lissajous} or \emph{Bowditch} curve.

	\item What interesting curves did you find?

	\ea 
\end{activitySolution}
\aftera
