\begin{exercises} 
	\item A rectangular box with a square bottom and closed top is to be made from two materials.  The material for the side costs \$1.50 per square foot and the material for the bottom costs \$3.00 per square foot.  If you are willing to spend \$15 on the box, what is the largest volume it can contain?  Justify your answer completely using calculus.
	\item A farmer wants to start raising cows, horses, goats, and sheep, and desires to have a rectangular pasture for the animals to graze in.  However, no two different kinds of animals can graze together.  In order to minimize the amount of fencing she will need, she has decided to enclose a large rectangular area and then divide it into four equally sized pens, or grazing areas.  She has decided to purchase 7500 ft of fencing.  What is the maximum possible area that each of the four pens will enclose?
	\item Two vertical towers of heights 60 ft and 80 ft stand on level ground, with their bases 100 ft apart.  A cable that is stretched from the top of one pole to some point on the ground between the poles, and then to the top of the other pole.   What is the minimum possible length of cable required?  Justify your answer completely using calculus.
	\item A company is designing propane tanks that are cylindrical with hemispherical ends.   Assume that the company wants tanks that will hold 1000 cubic meters of gas, and that the ends are more expensive to make, costing \$5 per square foot, while the cylindrical barrel between the ends costs \$2 per square foot.  Use calculus to determine the minimum cost to construct such a tank.
\end{exercises}
\afterexercises