\begin{exercises} 
  \item Let $f(t) = te^{-2t}$ and $F(x) = \int_0^x f(t)$.
  	\ba
		\item Determine $F'(x)$.
		\item Use the First FTC to find a formula for $F$ that does not involve an integral.
		\item Is $F$ an increasing or decreasing function for $x > 0$?  Why?
	\ea	
	
  \item Consider the indefinite integral given by $\int e^{2x} \cos(e^x) \, dx$.
  	\ba
		\item Noting that $e^{2x} = e^x \cdot e^x$, use the substitution $z = e^{x}$ to determine a new, equivalent integral in the variable $z$.
		\item Evaluate the integral you found in (a) using an appropriate technique.
		\item How is the problem of evaluating $\int e^{2x} \cos(e^{2x}) \, dx$ different from evaluating the integral in (a)?  Do so.
		\item Evaluate each of the following integrals as well, keeping in mind the approach(es) used earlier in this problem:
		\begin{itemize}
			\item $\int e^{2x} \sin(e^x) \, dx$
			\item $\int e^{3x} \sin(e^{3x}) \, dx$
			\item $\int xe^{x^2} \cos(e^{x^2}) \sin(e^{x^2}) \, dx$
		\end{itemize}
	\ea
	
	
  \item For each of the following indefinite integrals, determine whether you would use $u$-substitution, integration by parts, neither, or both to evaluate the integral.  In each case, write one sentence to explain your reasoning, and include a statement of any substitutions used.  (That is, if you decide in a problem to let $u = e^{3x}$, you should state that, as well as that $du = 3e^{3x} \, dx$.)  Finally, use your chosen approach to evaluate each integral.
\end{exercises}
	\ba
		\item $\int x^2 \cos(x^3) \, dx$
		\item $\int x^4 \cos(x^3) \, dx$ \ \ (Hint: $x^4 = x^2 \cdot x^2$)
		\item $\int x\ln(x^2) \, dx$
		\item $\int \sin(x^4) \, dx$
		\item $\int x^3 \sin(x^4) \, dx$
		\item $\int x^7 \sin(x^4) \, dx$
	\ea

\afterexercises
