\begin{exercises} 
  \item Consider the definite integral $\int_0^1 x \tan(x) \, dx$.
  \ba
  	\item Explain why this integral cannot be evaluated exactly by using either $u$-substitution or by integrating by parts.
	\item Using 4 subintervals, compute $L_4$, $R_4$, $M_4$, $T_4$, and $S_4$.  
	\item Which of the approximations in (b) is an over-estimate to the true value of $\int_0^1 x \tan(x) \, dx$?  Which is an under-estimate?  How do you know?
  \ea
  
  \item For an unknown function $f(x)$, the following information is known.  
  \begin{itemize}
  	\item $f$ is continuous on $[3,6]$;
	\item $f$ is either always increasing or always decreasing on $[3,6]$;
	\item $f$ has the same concavity throughout the interval $[3,6]$;
	\item As approximations to $\int_3^6 f(x) \, dx$, $L_4 = 7.23$, $R_4 = 6.75$, and $M_4 = 7.05$.
  \end{itemize}
  \ba
  	\item Is $f$ increasing or decreasing on $[3,6]$?  What data tells you?
	\item Is $f$ concave up or concave down on $[3,6]$?  Why?
	\item Determine the best possible estimate you can for $\int_3^6 f(x) \, dx$, based on the given information.
  \ea
  
  \item The rate at which water flows through Table Rock Dam on the White River in Branson, MO, is measured in thousands of cubic feet per second (TCFS).  As engineers open the floodgates, flow rates are recorded according to the following chart.
  \begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
seconds, $t$ & 0 & 10 & 20 & 30 & 40 & 50 & 60 \\
\hline
flow in TCFS, $r(t)$ & 2000 & 2100 & 2400 & 3000 & 3900 & 5100 & 6500 \\
\hline
\end{tabular}
\end{center}
	\ba
		\item What definite integral measures the total volume of water to flow through the dam in the 60 second time period provided by the table above?
		\item Use the given data to calculate $M_n$ for the largest possible value of $n$ to approximate the integral you stated in (a).  Do you think $M_n$ over- or under-estimates the exact value of the integral?  Why?
		
		\item Approximate the integral stated in (a) by calculating $S_n$ for the largest possible value of $n$, based on the given data.
		
		\item Compute $\frac{1}{60} S_n$ and $\frac{2000+2100+2400+3000+3900+5100+6500}{7}$.  What quantity do both of these values estimate?  Which is a more accurate approximation?
	\ea
\end{exercises}
\afterexercises
