\begin{exercises} 
  \item  The logistic equation may be used to model how a rumor spreads
    through a group of people.  Suppose that $p(t)$ is the fraction of
    people that have heard the rumor on day $t$.  The equation
    $$
    \frac{dp}{dt} = 0.2p(1-p)
    $$
    describes how $p$ changes.  Suppose initially that one-tenth of
    the people have heard the rumor; that is, $p(0) = 0.1$.

    \ba
    \item What happens to $p(t)$ after a very long time?

    \item Determine a formula for the function $p(t)$.

    \item At what time is $p$ changing most rapidly?

    \item How long does it take before 80\% of the people have heard
      the rumor?

      \ea

  \item Suppose that $b(t)$ measures the number of bacteria living in
    a colony in a Petri dish, where $b$ is measured in thousands and
    $t$ is measured in days.  One day, you measure that there are
    6,000 bacteria and the per capita growth rate is 3.  A few days
    later, you measure that there are 9,000 bacteria and the per
    capita growth rate is 2.  

    \ba
  \item Assume that the per capita growth rate 
    $\frac{db/dt}{b}$ is a linear function of $b$.  Use the
    measurements to find this function and write a logistic equation
    to describe $\frac{db}{dt}$.

  \item What is the carrying capacity for the bacteria?

  \item At what population is the number of bacteria increasing most
    rapidly?
    
  \item If there are initially 1,000 bacteria, how long will it take
    to reach 80\% of the carrying capacity?

    \ea

  \item 
    Suppose that the population of a species of fish is controlled by
    the logistic equation
    $$
    \frac{dP}{dt} = 0.1P(10 - P),
    $$
    where $P$ is measured in thousands of fish and $t$ is measured in
    years.  

    \ba
    \item What is the carrying capacity of this population?

    \item Suppose that a long time has passed and that the fish
      population is stable at the carrying capacity.  At this time,
      humans begin harvesting 20\% of the fish every year.  Modify the
      differential equation by adding a term to incorporate the
      harvesting of fish.

    \item What is the new carrying capacity?

    \item What will the fish population be one year after the
      harvesting begins?

    \item How long will it take for the population to be within 10\%
      of the carrying capacity?
    \ea

\end{exercises}
\afterexercises


